---
title: "SELECTING TOP CAND FOR DS and WebDev"
author: "NITHIN C"
date: "17/02/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

importing required libraries

```{r }
library(openxlsx) #for opening xlsx files
library(tidyverse) #to clean and Process
library(tidyr)# data munging
library(dplyr)
movo<-read.xlsx("mv.xlsx",startRow = 1)
```


WE RENAMES THE COLNAMES TO SIMPLIFY THE TASK..
```{r warning=TRUE}
colnames(movo)
sapply(movo,class)
 movo<- movo %>% rename(APK_ID=Application_ID,City=Current.City,Python=`Python.(out.of.3)`)
```

I rename the observations for ease of use(FEATURE ENGINEERING)

```{r}
 movo <- movo %>% rename(R=`R.Programming.(out.of.3)`)

movo <- movo %>% rename(PHP=`PHP.(out.of.3)`)

movo <- movo %>% rename(DL = `Deep.Learning.(out.of.3)`)
 movo <- movo %>% rename(MYSQL=`MySQL.(out.of.3)`) 
 movo1 <- movo %>% rename(HTML=`HTML.(out.of.3)`)
 movo <- movo %>% rename(JavaScript=`JavaScript.(out.of.3)`)
movo <- movo %>% rename(AJAX=`AJAX.(out.of.3)`)
 movo <- movo %>% rename(CSS=`CSS.(out.of.3)`)
 movo <- movo %>% rename(Bootstrap=`Bootstrap.(out.of.3)`)
 movo <- movo %>% rename(MongoDB=`MongoDB.(out.of.3)`)
 movo <- movo %>% rename(NodeJS=`Node.js.(out.of.3)`)
 movo <- movo %>% rename(ReactJS=`ReactJS.(out.of.3)`)
```

```{r}
 
movo <- movo %>% rename(HTML=`HTML.(out.of.3)`)
colnames(movo)

```
 HERE WE SEGREGATE THE COLUMNS THAT ARE MOST RELEVANT TO DATA_SCIENCE

```{r}
 data_scientist<-select(movo,APK_ID,City,Python:DL,MYSQL,MongoDB,Degree,Stream,Performance_UG,Performance_PG,Performance_10,Performance_12)
colnames(data_scientist)
```
 
  HERE WE SEGREGATE THE COLUMNS THAT ARE MOST RELEVANT TO WEB_DEVELOPMENT

 
```{r }
 Web_Development<-select(movo,APK_ID,City,Python,MYSQL,HTML,CSS,JavaScript,AJAX,Bootstrap,MongoDB,NodeJS,ReactJS,Degree,Stream,Performance_PG,Performance_UG,Performance_12,Performance_10)


```
 
```{r }
 colnames(Web_Development)
```

AS WE NOW THE LEVELS 0=NO KNOWLDGE ,1= BEGINNER ,2=INTERMEDIATE ,3= PROFICIENT

HENCE WE MULTIPLY THE ATTRIBUTES WITH PRE_DEFINED NUMBER TO MATCH THE MOST REQUIRED CANDIDATE BASED ON THE IMPORTANCE OF THE LANGUAGE AND IT'S POPULARITY.

```{r}
 Web_Development$MYSQL<-4*(Web_Development$MYSQL)
``` 

```{r}
 Web_Development$JavaScript<-5*(Web_Development$JavaScript)
 Web_Development$HTML<-3*(Web_Development$HTML)
 Web_Development$CSS<-3.5*(Web_Development$CSS)
 Web_Development$AJAX<-2.5*(Web_Development$AJAX)
 Web_Development$MongoDB<-2.8*(Web_Development$MongoDB)
 Web_Development$NodeJS<-1.8*(Web_Development$NodeJS)
 Web_Development$ReactJS<-1.0*(Web_Development$ReactJS)
```
 
```{r }
 data_scientist$Python<-4*(data_scientist$Python)
 data_scientist$DL<-5*(data_scientist$DL)
 data_scientist$R<-4*(data_scientist$R)
 data_scientist$MYSQL<-2*(data_scientist$MYSQL)
 data_scientist$MongoDB<-2.5*(data_scientist$MongoDB) 
```
 
```{r }
 data_scientist$Performance_10<-gsub("(.*)/.*","\\1",data_scientist$Performance_10)
  data_scientist$Performance_12<-gsub("(.*)/.*","\\1",data_scientist$Performance_12)
  data_scientist$Performance_UG<-gsub("(.*)/.*","\\1",data_scientist$Performance_UG)
  data_scientist$Performance_PG<-gsub("(.*)/.*","\\1",data_scientist$Performance_PG)
```
  
```{r }
  Web_Development$Performance_10<-gsub("(.*)/.*","\\1",Web_Development$Performance_10)
   Web_Development$Performance_12<-gsub("(.*)/.*","\\1",Web_Development$Performance_12)
  Web_Development$Performance_PG<-gsub("(.*)/.*","\\1",Web_Development$Performance_PG)
    Web_Development$Performance_UG<-gsub("(.*)/.*","\\1",Web_Development$Performance_UG)
```

HERE WE CREATE A NEW COLUMN FOR DATA_SCIENTIST CALLED TOTAL WHICH IS THE SUM(PYTHON,R,MYSQL,DL,MONGODB)

AGAIN WE CREATE A NEW COLUMN FOR WEB_DEVELOPMENT CALLED TOTAL WHICH IS THE SUM(PYTHON,MYSQL,HTML,CSS,JAVASCRIPT,AJAX,BOOTSTRAP,MONGODB,NODEJS,REACTJS

```{r}
Web_Development["Total"]=rowSums(Web_Development[,3:12])

data_scientist["Total"]=rowSums(data_scientist[,3:7])
```


HERE WE SORT THE VALUES IN DECREASING ORDER ON THE VALUE OF TOTAL FOR BOTH DATA_SCIENCE AND WEB_DEVELOPMENT


```{r}
colnames(data_scientist)
summary(data_scientist)
IQR(data_scientist$Total)
data_scientist<-mutate(data_scientist,SCORE_ON_AVG=Total-mean(Total,na.rm=T))
head(data_scientist,3)
summary(data_scientist)

data_scientist["SELECTION_STATUS"]=if_else(movo$Total>=IQR(data_scientist$Total),"YES","NO")
datadsdev_interns <- data_scientist[order(data_scientist[,"Total"],decreasing = T),]
 head(datadsdev_interns,9)
```
```{r}
colnames(Web_Development)
summary(Web_Development)
IQR(Web_Development$Total)
Web_Development<-mutate(Web_Development,SCORE_ON_AVG=Total-mean(Total,na.rm=T))
head(Web_Development,3)
summary(Web_Development)

Web_Development["SELECTION_STATUS"]=if_else(Web_Development$Total>=15,"YES","NO")
web_dev_TOP_10_interns <- Web_Development[order(Web_Development[,"Total"],decreasing = T),]
 head(web_dev_TOP_10_interns,10)
```
require

SUMMARY

IT IS NOT MANDATORY THAT EVERY DATASET MUST use A MACHINE LEARNING ALGORITH TO SOLVE A PROBLEM.HERE THE PROBLEM DESCRIPTION WAS TO HELP "INTERNBUDDY" SELECTING THEIR CANDIDATES FOR BOTH DATA_SCIENCE AND WEB_DEVELOPMENT ,THE ABOVE ANALYTICS SELECTS THE TOP 20 DATA_SCIENCE AND WEB_DEVELOPMENT BASED ON THEIR SCORES(TOTAL.)